The \textit{Kepler} Smear Campaign: Light curves for 102 Very Bright Stars

### 2019-03-20 paper/ms.tex
bedding updates

\title[The Kepler Smear Campaign]{The \textit{Kepler} Smear Campaign}

@@

% Beyond searching for planets, 
\kepler has revolutionized the field of asteroseismology both for solar-like oscillations \citep{2010PASP..122..131G,2010ApJ...713L.169C} and for coherent heat-engine driven oscillations \citep{2018arXiv180907779A}. It has yielded the detection of gravity-dominated mixed mode period spacings for red giants \citep{rggmodes,2014A&A...572L...5M}, enabling probes of interior rotation \citep{rggmoderotation,2012A&A...548A..10M,2012ApJ...756...19D} and distinguishing between hydrogen- and helium-burning cores \citep{rggmodehelium,2012A&A...540A.143M}. It has also permitted the determination of ages and fundamental parameters of cool main-sequence stars \citep{silvaages}, including planet-hosting stars \citep{huberplanetages,silvaaguirre2015,2016MNRAS.456.2183D,2018MNRAS.479.4786V}. \kepler gravity-mode asteroseismology has also been used to derive the internal rotation profiles of intermediate mass stars \citep{triana15,vanreeth18}. %revealing the most ancient known planetary system, dating back to the earliest stages of the galaxy \citep{ancientplanets}. %By comparing asteroseismic stellar ages to stellar rotation periods, \citet{angusgyro} have shown that gyrochronology models cannot fit the data with a single relation, leading~\citet{vansadersgyro}~to suggest a qualitative change in dynamo mechanism as stars age through the main-sequence.

A major outcome of the \kepler asteroseismology programme is a legacy sample of extremely well characterized stars that can serve as benchmarks for future work \citep{keplerlegacy1,silvaaguirre2017,silvaaguirre2015,2016MNRAS.456.2183D}. Asteroseismological studies with \kepler complement other probes of stellar physics well: for example, the APOKASC sample of~1916 spectroscopically- and asteroseismically-characterized red giant stars \citep{2014ApJS..215...19P}. For this APOKASC sample, \citet{hawkinsapogee} have been able to extract precise elemental abundances by fitting spectroscopic data with \logg and \teff fixed to asteroseismically-determined values. It is necessary to calibrate such a study against benchmark stars with very precisely-determined parameters, which in practice requires nearby bright stars that are amenable to very high signal-to-noise spectroscopy plus asteroseismology \citep{creeveybenchmark}, parallaxes \citep{hawkinsbenchmarks}, and/or interferometry \citep{casagrandebenchmark,creeveybenchmark2}. This is especially important in the context of the \gaia mission \citep{gaia}, which has recently put out its second data release of 1,692,919,135 sources, including 1,331,909,727 with parallaxes \citep{gaiadr2}. These data will form the basis of many large surveys and it is vital that they are calibrated correctly. To this end, 36~FGK stars including both giants and dwarfs have been chosen as \gaia benchmark stars for which metallicities \citep{gaiabenchmark1,2018RNAAS...2c.152J}, effective temperatures and asteroseismic surface gravities \citep{gaiabenchmark3}, and relative abundances of $\alpha$ and iron-peak elements \citep{gaiabenchmark4} have been determined. This includes only four main-sequence stars much cooler than the Sun, due to the paucity of such stars with asteroseismology. This has been accompanied by the release of high resolution spectra \citep{gaiabenchmark2} and formed the basis of extensions to lower metallicities \citep{gaiabenchmark5}, stellar twin studies \citep{gaiabenchmarktwins} and comparisons of stellar abundance determination pipelines \citep{gaiabenchmarkabundances}. Furthermore, by combining asteroseismology with optical interferometry, it has been possible to determine fundamental parameters of main-sequence and giant stars with unprecedented precision \citep{huber12,thetacygwhite,white15}.

Brighter \kepler stars are therefore ideal benchmark targets, since photometry can be most easily complemented by \gaia parallaxes, interferometric diameters, and high resolution spectroscopy.  
Unfortunately, the \kepler field was deliberately placed to minimize overall the number of extremely bright stars on the detectors, so that only a dozen stars brighter than~6th~magnitude landed on silicon \citep{2010ApJ...713L..79K}. This was because stars brighter than $Kp \sim 11$ saturate the CCD detectors, with their flux distributed along a bleed column and rendering those pixels otherwise unusable. Furthermore, due to the limited availablility of bandwidth to download data from the spacecraft, only $\sim 5.7\%$ of pixels on the \kepler detectors are actually downloaded in any one Quarter \citep{2010ApJ...713L..87J}. The result of these two target selection constraints is that photometry was obtained for most of the mission for only~35 stars brighter than $Kp<7$ in the \kepler field, while~17 targets in this range were observed for less than half the mission and~29 targets brighter than this threshold were entirely ignored. The availability of \kepler data remains significantly incomplete down to fainter magnitudes, and in this work we consider $Kp=9$ to be an arbitrary cutoff for bright stars of interest. In the \ktwo mission \citep{k2early}, very saturated stars have been observed with `halo photometry' using unsaturated pixels in a specially-determined region around bright stars, including the Pleiades \citep{halo}, Aldebaran \citep{aldebaran}, $\iota$~Librae \citep{Buysschaert2018}, and $\rho$~Leonis \citep{rholeo}. Unfortunately, in the four-year \kepler sample, photometry of such saturated stars was rarely attempted.

\citet{orig_smear} noted a way to obtain photometry of every target on-silicon in \kepler using a data channel normally used for calibration, even if active pixels were not allocated and downloaded. \kepler employs an inter-line transfer CCD as its detector, which successively shuffles each row of pixels down to the edges of the chip to be read out. Because the \kepler camera lacks a shutter, the detector is exposed to light during the readout process, with the result that fluxes in each pixel are contaminated by light collected from stars in the same column. This is a particularly serious issue for faint stars in the same detector column as brighter stars, and it is important to calibrate this at each readout stage. Six rows of blank `masked' pixels were allocated in each column to measure the smear bias; furthermore, six `virtual' rows were recorded at the end of the readout, with the result that twelve rows of pixels sample the smear bias in each column. \citet{orig_smear} realized that these encode the light curves of bright targets in a 1D projection of the star field. The masked and virtual smear registers each receive $\sim 1/1034$ of the incident flux in each column. If this is dominated by the light from a single star, the flux combining both smear registers is equivalent to the normal flux of a star $\sim 6.8$~magnitudes fainter.

In \citet{smear}, we demonstrated a method for extracting precise light curves of bright stars in \kepler and \ktwo from these collateral data, and presented light curves of a small number of variable stars as examples to illustrate this method. In this paper we present smear light curves of all unobserved or significantly under-observed stars brighter than $Kp=9$ in the \kepler field. This sample mostly consists of red giants and hot stars, containing only one~G dwarf. We find no transiting planets, but detect one new eclipsing binary, and measure solar-like oscillations in 33~red giants. We do not model main-sequence stars in great detail, but provide some discussion and initial classification of interesting variability. For the oscillating red giants that constitute the bulk of the sample, we determine the asteroseismic parameters \numax and \Dnu, and therefore stellar masses and \logg measurements. We have also obtained high-resolution optical spectroscopy of 63~stars, predominantly giants, with the Tillinghast Reflector \'{E}chelle Spectrograph \citep[TRES;][]{2007RMxAC..28..129S}. For the~33 stars with both spectroscopy and asteroseismic parameters we derive fundamental stellar parameters and elemental abundances. These asteroseismic constraints can be compared to those from \gaia, offering the opportunity both to test asteroseismic scaling relations and combine both datasets to refine the benchmark star properties further.

@@

We have obtained smear light curves for our sample of red giant stars with the \texttt{keplersmear} pipeline as described in Section~\ref{photometry}, performed asteroseismology on all of these to extract \numax and therefore \logg as described in Section~\ref{asteroseismology}, and combined these with TRES spectra to obtain chemical abundances as described in Section~\ref{spectroscopy}.

@@

We selected all stars on-silicon in \kepler with $Kp<9$ that were targeted for fewer than $8$ quarters. The majority of these were not previously targeted at all, but sixteen stars were to some extent observed conventionally: these are listed in Table~\ref{quarters}. A number of these lay at the edge of a detector, with the result that in some cadences the centroid of the star did not lie on the chip; light curves from these targets were found to be of extremely low quality and all of these stars were discarded. After applying these criteria we obtained a list of 102 targets, which are listed in Table~\ref{all_stars} with their \kepler magnitude $Kp$, together with their spectral type from SIMBAD, \gaia~DR2 apparent~$G$ magnitudes and $Bp-Rp$ colours, \gaia~DR2 calibrated distances from \citet{gaiadists}, variability classification and availability of TRES spectroscopy. The \kepler spacecraft rotates between quarters, so that it cycles through four orientation `seasons' each rotated from the last by $90^{\circ}$. Some stars were not on silicon for all seasons: we have only one season of HD~179394; two for HD~187277, HD~226754, V554~Lyr, and BD+47~2891; and three for BD+43~3064. The addition of our sample to the conventionally-observed stars makes the \kepler survey magnitude-complete down to $Kp=9$ for all stars on-silicon.

>>>>

\title[The Kepler Smear Campaign]{The \textit{Kepler} Smear Campaign: Light curves for 102 Very Bright Stars}

@@

% Beyond searching for planets, 
\kepler has revolutionized the field of asteroseismology both for solar-like oscillations \citep{2010PASP..122..131G,2010ApJ...713L.169C} and for coherent heat-engine driven oscillations \citep{2018arXiv180907779A}. It has yielded the detection of gravity-dominated mixed-mode period spacings for red giants \citep{rggmodes,2014A&A...572L...5M}, enabling probes of interior rotation \citep{rggmoderotation,2012A&A...548A..10M,2012ApJ...756...19D} and distinguishing between hydrogen- and helium-burning cores \citep{rggmodehelium,2012A&A...540A.143M}. It has also permitted the determination of ages and fundamental parameters of cool main-sequence stars \citep{silvaages}, including planet-hosting stars \citep{huberplanetages,silvaaguirre2015,2016MNRAS.456.2183D,2018MNRAS.479.4786V}. \kepler gravity-mode asteroseismology has also been used to derive the internal rotation profiles of intermediate mass stars \citep{triana15,vanreeth18}. %revealing the most ancient known planetary system, dating back to the earliest stages of the galaxy \citep{ancientplanets}. %By comparing asteroseismic stellar ages to stellar rotation periods, \citet{angusgyro} have shown that gyrochronology models cannot fit the data with a single relation, leading~\citet{vansadersgyro}~to suggest a qualitative change in dynamo mechanism as stars age through the main-sequence.

A major outcome of the \kepler asteroseismology programme is a legacy sample of extremely well-characterized stars that can serve as benchmarks for future work \citep{keplerlegacy1,silvaaguirre2017,silvaaguirre2015,2016MNRAS.456.2183D}. Asteroseismological studies with \kepler complement other probes of stellar physics, such as the APOKASC sample of~1916 spectroscopically- and asteroseismically-characterized red giant stars \citep{2014ApJS..215...19P}. For this APOKASC sample, \citet{hawkinsapogee} have been able to extract precise elemental abundances by fitting spectroscopic data with \logg and \teff fixed to asteroseismically-determined values. It is necessary to calibrate such a study against benchmark stars with very precisely-determined parameters, which in practice requires nearby bright stars that are amenable to very high signal-to-noise spectroscopy plus asteroseismology \citep{creeveybenchmark}, parallaxes \citep{hawkinsbenchmarks}, and/or interferometry \citep{casagrandebenchmark,creeveybenchmark2}. This is especially important in the context of the \gaia mission \citep{gaia}, which has recently put out its second data release of 1,692,919,135 sources, including 1,331,909,727 with parallaxes \citep{gaiadr2}. These data will form the basis of many large surveys and it is vital that they are calibrated correctly. To this end, 36~FGK stars including both giants and dwarfs have been chosen as \gaia benchmark stars for which metallicities \citep{gaiabenchmark1,2018RNAAS...2c.152J}, effective temperatures and asteroseismic surface gravities \citep{gaiabenchmark3}, and relative abundances of $\alpha$ and iron-peak elements \citep{gaiabenchmark4} have been determined. This includes only four main-sequence stars much cooler than the Sun, due to the paucity of such stars with asteroseismology. This has been accompanied by the release of high-resolution spectra \citep{gaiabenchmark2} and formed the basis of extensions to lower metallicities \citep{gaiabenchmark5}, stellar twin studies \citep{gaiabenchmarktwins} and comparisons of stellar abundance determination pipelines \citep{gaiabenchmarkabundances}. Furthermore, by combining asteroseismology with optical interferometry, it has been possible to determine fundamental parameters of main-sequence and giant stars with unprecedented precision \citep{huber12,thetacygwhite,white15}.

Brighter \kepler stars are therefore ideal benchmark targets, since photometry can be most easily complemented by \gaia parallaxes, interferometric diameters, and high-resolution spectroscopy.  
Unfortunately, the \kepler field was deliberately placed to minimize overall the number of extremely bright stars on the detectors, so that only a dozen stars brighter than~6th~magnitude landed on silicon \citep{2010ApJ...713L..79K}. This was because stars brighter than $Kp \sim 11$ saturated the CCD detectors, with their flux distributed along a bleed column and rendering those pixels otherwise unusable. Furthermore, due to the limited bandwidth to download data from the spacecraft, only $\sim 5.7\%$ of pixels on the \kepler detectors were actually downloaded in each Quarter \citep{2010ApJ...713L..87J}. The result of these two target selection constraints is that photometry was obtained for most of the mission for only~35 stars brighter than $Kp<7$ in the \kepler field, while a further~17 targets in this range were observed for less than half the mission and~29 targets brighter than this threshold were entirely ignored. The availability of \kepler data remains significantly incomplete down to fainter magnitudes, and in this work we consider $Kp=9$ to be an arbitrary cutoff for bright stars of interest. In the \ktwo mission \citep{k2early}, very saturated stars have been observed with `halo photometry' using unsaturated pixels in a specially-determined region around bright stars, including the Pleiades \citep{halo}, Aldebaran \citep{aldebaran}, $\iota$~Librae \citep{Buysschaert2018}, and $\rho$~Leonis \citep{rholeo}. Unfortunately, in the four-year \kepler sample, photometry of such saturated stars was rarely attempted, with some exceptions, such as RR~Lyrae \citep{Kolenberg2011} and $\theta$~Cyg and 16~Cyg~AB \citep[e.g.][]{thetacygwhite,Guzik2016}.

\citet{orig_smear} noted a way to obtain photometry of every target on-silicon in \kepler using a data channel normally used for calibration, even if active pixels were not allocated and downloaded. \kepler employs an inter-line transfer CCD, which successively shuffles each row of pixels to the edges of the chip to be read out. Because the \kepler camera lacks a shutter, the detector is exposed to light during the readout process, with the result that fluxes in each pixel are contaminated by light collected from stars in the same column. This is a particularly serious issue for faint stars in the same detector column as brighter stars, and it is important to calibrate this at each readout stage. Six rows of blank `masked' pixels were allocated in each column to measure the smear bias; furthermore, six `virtual' rows were recorded at the end of the readout, with the result that twelve rows of pixels sample the smear bias in each column. \citet{orig_smear} realized that these encode the light curves of bright targets in a 1D projection of the star field. The masked and virtual smear registers each receive $\sim 1/1034$ of the incident flux in each column. If this is dominated by the light from a single star, the flux combining both smear registers is equivalent to the normal flux of a star $\sim 6.8$~magnitudes fainter.

In \citet{smear}, we demonstrated a method for extracting precise light curves of bright stars in \kepler and \ktwo from these collateral data, and presented light curves of a small number of variable stars as examples to illustrate this method. In this paper we present smear light curves of all unobserved or significantly under-observed stars brighter than $Kp=9$ in the \kepler field. This sample mostly consists of red giants and hot stars, containing only one~G dwarf. We find no transiting planets, but detect one new eclipsing binary, and measure solar-like oscillations in 33~red giants. We do not model the hot main-sequence stars in great detail, but provide some discussion and initial classification of interesting variability. For the oscillating red giants that constitute the bulk of the sample, we determine the asteroseismic parameters \numax and \Dnu, and therefore stellar masses and \logg measurements. We have also obtained high-resolution optical spectroscopy of 63~stars, predominantly giants, with the Tillinghast Reflector \'{E}chelle Spectrograph \citep[TRES;][]{2007RMxAC..28..129S}. For the~33 stars with both spectroscopy and asteroseismic parameters we derive fundamental stellar parameters and elemental abundances. These asteroseismic constraints can be compared to those from \gaia, offering the opportunity both to test asteroseismic scaling relations and combine both datasets to refine the benchmark star properties further.

@@

@@

We selected all stars on-silicon in \kepler with $Kp<9$ that were targeted for fewer than $8$ quarters. The majority of these were not previously targeted at all, but sixteen stars were to some extent observed conventionally; these are listed in Table~\ref{quarters}. A number of these lay at the edge of a detector, with the result that in some cadences the centroid of the star did not lie on the chip; light curves from these targets were found to be of extremely low quality and all of these stars were discarded. After applying these criteria we obtained a list of 102 targets, which are listed in Table~\ref{all_stars} with their \kepler magnitude $Kp$, together with their spectral type from SIMBAD, \gaia~DR2 apparent~$G$ magnitudes and $Bp-Rp$ colours, \gaia~DR2 calibrated distances from \citet{gaiadists}, variability classification and availability of TRES spectroscopy. The \kepler spacecraft rotates between quarters, so that it cycles through four orientation `seasons' each rotated from the last by $90^{\circ}$. Some stars were not on silicon for all seasons: we have only one season of HD~179394; two for HD~187277, HD~226754, V554~Lyr, and BD+47~2891; and three for BD+43~3064. The addition of our sample to the conventionally-observed stars makes the \kepler survey magnitude-complete down to $Kp=9$ for all stars on-silicon.
